openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Fix plot-lifespan-activity-cats

```{r plot-lifespan-activity-cats}
#TODO: Eliminate Infs

left_join(oarch_lifespan, oarch, by = c("item_name")) %>%
  drop_na(category) %>%
  group_by(category) %>%
  summarise(avg_lifespan = mean(lifespan),
            avg_commit_rate = mean(commit_rate)) ->
  oarch_lifespan_by_cat

>>>>

```{r plot-lifespan-activity-cats}
#TODO: Eliminate Infs
oarch_lifespan %>% 
  select(-category) %>% 
  left_join(oarch, by = c("item_name")) %>%
  drop_na(category) %>%
  group_by(category) %>%
  summarise(avg_lifespan = mean(lifespan),
            avg_commit_rate = mean(commit_rate)) ->
  oarch_lifespan_by_cat
